Analysis

### 2023-06-23 analysis/analysis.Rmd
update with edits for reviewers

```{r initialize_packages, message=FALSE}
library(morris)
library(broom)
library(knitr)
library(broman)
library(phyloseq)
library(knitr)
library(magrittr)
library(vegan)
library(ggpubr)
library(ggtext)
library(ALDEx2)
library(corncob)
library(ANCOMBC)
library(tidyverse)
library(here)
library(patchwork)
library(extrafont)

@@

# (p_response_cl <- ggplot(fluxes, aes(x = passage, y = log_ch4, color = treat)) +
#     stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x') +
#     scale_color_manual(
#       name = "Treatment", 
#       labels = c('Control', 'Selection'), 
#       values = c('gray40', 'darkorange2')) +
#     geom_jitter(#aes(alpha = selected), 
#       width = 0.1) + 
#         labs(x = "Passage Number", 
#                   y = expression(log[10] ~ CH[4] ~ "(-k)")) +
#   scale_x_continuous(labels = 1:5) +
#     coord_fixed(ratio))

@@

# ggsave(here(fig_dir, 'fig2.jpg'), p_response, width = 4, height = 3)
# ggsave(here(fig_dir, 'fig2.svg'), p_response, width = 4, height = 3)
# ggsave(here(fig_dir, 'fig2_cl.png'), p_response_cl, width = 4, height = 3)

@@

ggsave(here(fig_dir, 'fig2.eps'), p_response_bw, width = 88, height = 65, units = 'mm', device = cairo_ps)
# embed_fonts(here(fig_dir, 'fig2_bw.eps'))

@@

# ggsave(here(fig_dir, "fig3.png"), width = 8*.9, height = 4*.9)
# ggsave(here(fig_dir, "fig3.svg"), width = 8*.9, height = 4*.9)
ggsave(here(fig_dir, "fig3.eps"),
       p_rh,
       width = 88,
       height = 45, 
       units = 'mm',
       device = cairo_ps)
# ggsave(here(fig_dir, "fig3.eps"), 
#        p_rh,
#        width = 5,
#        height = 2.5)
# save(rh_model, file = here(der_dir, 'herit_model.RData'))

@@

centroids <-
  nmds_data %>% 
  group_by(passage, treat) %>% 
  summarize(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2),
            .groups = "drop")
# p_beta_cl <-
#   nmds_data %>%   
#   ggplot(aes(x = NMDS1, y = NMDS2, shape = passage, color = treat)) +
#   geom_point() +
#   stat_ellipse(show.legend = FALSE) +
#   coord_fixed() +
#   scale_shape_discrete(name = "Passage", labels = c(2, 5)) +
#   scale_color_manual(name = "Treatment",
#                        labels = c('Control', 'Selection'),
#                        values = c('gray40', 'darkorange2')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())
  #   
# pcoa <- cmdscale(rare_dist_bray, eig = TRUE, add = TRUE)
# round(pcoa$eig*100/sum(pcoa$eig),1)
# pcoa_per_exp <- 100 * eigenvals(pcoa) / sum(eigenvals(pcoa))
# 
# ratio = pcoa_per_exp[2]/pcoa_per_exp[1]
# 
# pcoa_scores <-
#   scores(pcoa, display = "sites") %>%
#   as_tibble(rownames = "sample")
# 
# pcoa_data <-
#   aes_data %>%
#   select(sample, passage, treat) %>%
#   distinct %>%
#   inner_join(pcoa_scores, by = "sample")
# 
# # p_beta <-
#   pcoa_data %>%
#   ggplot(aes(x = Dim1, y = Dim2, shape = passage, color = treat)) +
#   geom_point() +
#   stat_ellipse(show.legend = FALSE) +
#   coord_fixed(ratio) +
#   scale_shape_discrete(name = "Passage", labels = c(2, 5)) +
#   scale_color_manual(name = "Treatment",
#                        labels = c('Neutral', 'Positive'),
#                        values = c('gray40', 'darkorange2')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())

@@

# ggsave(here(fig_dir, 'fig4.png'), p_beta, height = 2.5, width = 4) 
# ggsave(here(fig_dir, 'fig4.svg'), p_beta, height = 2.5, width = 4) 
# ggsave(here(fig_dir, 'fig4_cl.png'), p_beta_cl, height = 2.5, width = 4)

(p_beta_bw <-
  nmds_data %>%   
  ggplot(aes(x = NMDS1, y = NMDS2, shape = passage, fill = treat, 
             # linetype = treat
             )) +
  geom_point() +
  # stat_ellipse(
  #     # show.legend = FALSE
  #     ) +
  #   scale_linetype_manual(
  #     name = "Treatment", 
  #     labels = c('Control', 'Selection'), 
  #     values = c(3, 1)) +
  coord_fixed() +
  scale_shape_manual(name = "Passage", 
                     labels = c(2, 5),
                     values = c(24, 21)) +
  scale_fill_manual(name = "Treatment",
                       labels = c('Control', 'Selection'),
                       values = c('white', 'black')) +
  guides(fill=guide_legend(override.aes = list(shape=21)))
  # scale_color_manual(name = "Treatment",
  #                      labels = c('Neutral', 'Positive'),
  #                      values = c('white', 'black')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())
  #   
)
ggsave(here(fig_dir, 'fig4.eps'), 
       p_beta_bw, 
       height = 60,
       width = 180,
       # height = 60,
       # width = 88,
       units = 'mm', 
       device = cairo_ps
       )

@@

aes_family_G5 <-
  aes_G5 %>% 
  select(asv, sample, treat, count, Family) %>%
  group_by(sample, Family) %>% 
  mutate(total = sum(count)) %>% 
  ungroup() %>% 
  select(sample, treat, Family, total) %>% 
  distinct()

@@

sample_data <- aes_family_G5 %>% 
  select(sample, treat) %>% 
  distinct() %>% 
  as.data.frame()

@@

@@

da_analysis <- differentialTest(formula = ~ treat,
                                phi.formula = ~ 1,
                                formula_null = ~ 1,
                                phi.formula_null = ~ 1,
                                test = "Wald", 
                                boot = FALSE,
                                data = otu_table,
                                sample_data = sample_data,
                                fdr_cutoff = 0.05, B = 100,
                                taxa_are_rows = TRUE)

@@

dt_plot <- function(dt_data) {
  ggplot(dt_data, aes(x = x, xmin = xmin, xmax = xmax, y = reorder(taxa, x))) +
    geom_pointrange() +
    geom_vline(xintercept = 0) +
    labs(x = "Estimate", y = NULL) +
    coord_cartesian(clip="off") +
    # theme(panel.border = element_blank()) +
    theme_classic() +
      theme(axis.text.y = element_markdown())

}

@@

all_taxa$Family <- factor(all_taxa$Family, levels = sort_order$Family)
all_iqm$Family <- factor(all_iqm$Family, levels = sort_order$Family)
all_taxa <-
  all_taxa %>% 
  mutate(direction = if_else(effect > 0, 0, 1))
all_iqm <-
all_taxa %>% 
  select(Family, direction) %>% 
  distinct() %>% 
  full_join(all_iqm, by = "Family")
# (p_log10_cl <-
# 	all_taxa %>%
# 	ggplot(aes(x = rel_abund, y = Family, color = treat)) +
# 	geom_point(position=position_jitterdodge()) +
# 	geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, fill = treat), 
# 			data = all_iqm, 
# 			position = position_dodge(width = 0.75), 
# 			shape = 21, 
# 			color = "black") +
# 	theme_bw() +
# 	theme(axis.text.y = element_markdown()) +
# 	labs(x = "Relative Abundance (%)", y = NULL) +
# 	scale_color_manual(name = "Treatment",
# 			   labels = c('Control', 'Selection'),
# 			   values = c('gray40', 'darkorange2')) +
# 	scale_fill_manual(name = "Treatment",
# 			   labels = c('Control', 'Selection'),
# 			   values = c('gray40', 'darkorange2')) +
#     facet_grid(direction ~ ., scale = "free_y", space = "free")  + 
# theme(
#   strip.background = element_blank(),
#   strip.text.y = element_blank()
# ) +
# 	scale_x_log10(breaks = c(0.001, 0.01, 0.1, 1),
# 		      labels = c(0.001, 0.01, 0.1, 1)))

@@

# ggsave(here(fig_dir, 'fig5.jpg'), p_log10, width = 5, height = 5)
# ggsave(here(fig_dir, 'fig5.svg'), p_log10, width = 5, height = 5)
# ggsave(here(fig_dir, 'fig5_cl.png'), p_log10_cl, width = 5, height = 5)
(p_log10_bw <-
	all_taxa %>%
	ggplot(aes(x = rel_abund, y = Family, fill = treat)) +
	geom_point(position=position_jitterdodge(jitter.width = 0.1,
	                                         dodge.width = 0.4), shape = 21, size = 1) +
        theme_bw(base_size = 7) +
            theme(panel.border = element_rect(fill = NA, linewidth = 1.0625),
                  axis.line = element_blank(),
                  text = element_text(family = 'Arial')) +
	# geom_jitter(shape = 21, height = 0.1) +
	# geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, color = treat), 
	# 		data = all_iqm, 
	# 		position = position_dodge(width = 0.75), 
	# 		shape = 21, 
	# 		# color = "black"
	# 		) +
	# theme_bw() +
	theme(axis.text.y = element_markdown()) +
	labs(x = "Relative Abundance (%)", y = NULL) +
	# scale_color_manual(name = "Treatment",
	# 		   labels = c('Control', 'Selection'),
	# 		   values = c('black', 'gray')) +
	scale_fill_manual(name = "Treatment",
			   labels = c('Control', 'Selection'),
			   values = c('white', 'black')) +
    facet_grid(direction ~ ., 
               scale = "free_y",
               space = "free")  + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank()) +
	scale_x_log10(breaks = c(0.001, 0.01, 0.1, 1),
		      labels = c(0.001, 0.01, 0.1, 1))
    )
ggsave(here(fig_dir, 'fig5.eps'), 
       p_log10_bw, 
       width = 100, 
       height = 88,
       units = 'mm',
       device = cairo_ps
       )

@@

>>>>

```{r initialize_packages, message=FALSE}
library(morris)
library(broom)
library(knitr)
library(broman)
library(phyloseq)
library(knitr)
library(magrittr)
library(vegan)
library(ggpubr)
library(ggtext)
library(ALDEx2)
library(corncob)
library(ANCOMBC)
library(here)
library(patchwork)
library(extrafont)
library(tidyverse)

@@

(p_response_cl <- ggplot(fluxes, aes(x = passage, y = log_ch4, color = treat)) +
    stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x',
                linewidth = 0.5) +
    scale_color_manual(
      name = "Treatment",
      labels = c('Control', 'Selection'),
      values = c('gray40', 'darkorange2')) +
    geom_jitter(#aes(alpha = selected),
      width = 0.1,
      size = 0.5) +
        labs(x = "Passage Number",
                  y = expression(log[10] ~ CH[4] ~ "(-k)")) +
  scale_x_continuous(labels = 1:5) +
    coord_fixed(ratio))

@@

ggsave(here(fig_dir, 'fig2.png'), p_response_cl, width = 88, height = 65, units = 'mm')
# ggsave(here(fig_dir, 'fig2.svg'), p_response, width = 4, height = 3)
# ggsave(here(fig_dir, 'fig2_cl.png'), p_response_cl, width = 4, height = 3)

@@

# ggsave(here(fig_dir, 'fig2.eps'), p_response_bw, width = 88, height = 65, units = 'mm', device = cairo_ps)
# embed_fonts(here(fig_dir, 'fig2_bw.eps'))

@@

# ggsave(here(fig_dir, "fig3.png"), width = 8*.9, height = 4*.9)
# ggsave(here(fig_dir, "fig3.svg"), width = 8*.9, height = 4*.9)
# ggsave(here(fig_dir, "fig3.eps"),
#        p_rh,
#        width = 88,
#        height = 45, 
#        units = 'mm',
#        device = cairo_ps)
# ggsave(here(fig_dir, "fig3.eps"), 
#        p_rh,
#        width = 5,
#        height = 2.5)
# save(rh_model, file = here(der_dir, 'herit_model.RData'))

@@

centroids <-
  nmds_data %>% 
  group_by(passage, treat) %>% 
  summarize(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2),
            .groups = "drop")
(p_beta_cl <-
  nmds_data %>%
  ggplot(aes(x = NMDS1, y = NMDS2, shape = passage, color = treat)) +
  geom_point() +
  # stat_ellipse(show.legend = FALSE) +
  coord_fixed() +
  scale_shape_discrete(name = "Passage", labels = c(2, 5)) +
  scale_color_manual(name = "Treatment",
                       labels = c('Control', 'Selection'),
                       values = c('gray40', 'darkorange2'))) #+
# theme_bw() +
# theme(
#   plot.background = element_blank(),
#   panel.grid.major = element_blank(),
#   panel.grid.minor = element_blank())

# pcoa <- cmdscale(rare_dist_bray, eig = TRUE, add = TRUE)
# round(pcoa$eig*100/sum(pcoa$eig),1)
# pcoa_per_exp <- 100 * eigenvals(pcoa) / sum(eigenvals(pcoa))
# 
# ratio = pcoa_per_exp[2]/pcoa_per_exp[1]
# 
# pcoa_scores <-
#   scores(pcoa, display = "sites") %>%
#   as_tibble(rownames = "sample")
# 
# pcoa_data <-
#   aes_data %>%
#   select(sample, passage, treat) %>%
#   distinct %>%
#   inner_join(pcoa_scores, by = "sample")
# 
# # p_beta <-
#   pcoa_data %>%
#   ggplot(aes(x = Dim1, y = Dim2, shape = passage, color = treat)) +
#   geom_point() +
#   stat_ellipse(show.legend = FALSE) +
#   coord_fixed(ratio) +
#   scale_shape_discrete(name = "Passage", labels = c(2, 5)) +
#   scale_color_manual(name = "Treatment",
#                        labels = c('Neutral', 'Positive'),
#                        values = c('gray40', 'darkorange2')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())

@@

ggsave(here(fig_dir, 'fig3.png'), p_beta_cl,
       height = 60,
       width = 180,
       units = 'mm')
# ggsave(here(fig_dir, 'fig4.svg'), p_beta, height = 2.5, width = 4) 
# ggsave(here(fig_dir, 'fig4_cl.png'), p_beta_cl, height = 2.5, width = 4)

(p_beta_bw <-
  nmds_data %>%   
  ggplot(aes(x = NMDS1, y = NMDS2, shape = passage, fill = treat, 
             # linetype = treat
             )) +
  geom_point() +
  # stat_ellipse(
  #     # show.legend = FALSE
  #     ) +
  #   scale_linetype_manual(
  #     name = "Treatment", 
  #     labels = c('Control', 'Selection'), 
  #     values = c(3, 1)) +
  coord_fixed() +
  scale_shape_manual(name = "Passage", 
                     labels = c(2, 5),
                     values = c(24, 21)) +
  scale_fill_manual(name = "Treatment",
                       labels = c('Control', 'Selection'),
                       values = c('white', 'black')) +
  guides(fill=guide_legend(override.aes = list(shape=21)))
  # scale_color_manual(name = "Treatment",
  #                      labels = c('Neutral', 'Positive'),
  #                      values = c('white', 'black')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())
  #   
)
# ggsave(here(fig_dir, 'fig3.eps'), 
#        p_beta_cl, 
#        height = 60,
#        width = 180,
#        # height = 60,
#        # width = 88,
#        units = 'mm', 
#        device = cairo_ps
#        )

@@

aes_family_G5 <-
  aes_G5 %>% 
  select(asv, sample, treat, passage, count, Family) %>%
  group_by(sample, Family) %>% 
  mutate(total = sum(count)) %>% 
  ungroup() %>% 
  select(sample, treat, passage, Family, total) %>% 
  distinct()

# prevalent_families <- 
#   aes_family_G5 %>% 
#   group_by(Family) %>% 
#   summarize(prev = sum(total > 0), .groups = "drop") %>% 
#   filter(prev / 48 > 0.1) %$%
#   Family

@@

sample_data <- aes_family_G5 %>% 
  select(sample, treat, passage) %>% 
  distinct() %>% 
  as.data.frame()

@@

# ps <- phyloseq(sample_data = sample_data(sample_data), 
#                otu_table = otu_table(otu_table,
#                taxa_are_rows = TRUE))

@@

da_analysis <- differentialTest(formula = ~ treat,
                                phi.formula = ~ treat,
                                formula_null = ~ 1,
                                phi.formula_null = ~ treat,
                                test = "Wald", 
                                boot = FALSE,
                                data = otu_table,
                                sample_data = sample_data,
                                fdr_cutoff = 0.05, B = 100,
                                taxa_are_rows = TRUE)

@@

dt_plot <- function(dt_data) {
  ggplot(dt_data, aes(x = x, xmin = xmin, xmax = xmax, y = reorder(taxa, x))) +
        facet_wrap(~ variable) +
    geom_pointrange() +
    geom_vline(xintercept = 0) +
    labs(x = "Estimate", y = NULL) +
    coord_cartesian(clip="off") +
    # theme(panel.border = element_blank()) +
    theme_classic() +
      theme(axis.text.y = element_markdown())

}
# dt_plot <- function(dt_data) {
#   ggplot(dt_data, aes(x = x, xmin = xmin, xmax = xmax, y = reorder(taxa, x))) +
#     geom_pointrange() +
#     geom_vline(xintercept = 0) +
#     labs(x = "Estimate", y = NULL) +
#     coord_cartesian(clip="off") +
#     # theme(panel.border = element_blank()) +
#     theme_classic() +
#       theme(axis.text.y = element_markdown())
#     
#   
# }

@@

all_taxa$Family <- factor(all_taxa$Family, levels = sort_order$Family)
all_iqm$Family <- factor(all_iqm$Family, levels = sort_order$Family)
all_taxa <-
  all_taxa %>% 
  mutate(direction = if_else(effect > 0, 0, 1))
all_iqm <-
all_taxa %>% 
  select(Family, direction) %>% 
  distinct() %>% 
  full_join(all_iqm, by = "Family")

(p_log10_cl <-
	all_taxa %>%
	ggplot(aes(x = rel_abund, y = Family, color = treat)) +
	geom_point(position=position_jitterdodge(jitter.width = 0.1,
	                                         dodge.width = 0.4), size = 0.5) +	
        # geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, fill = treat),
			# data = all_iqm,
			# position = position_dodge(width = 0.75),
			# shape = 21,
			# color = "black") +
	theme_bw(base_size = 7) +
	theme(axis.text.y = element_markdown()) +
	labs(x = "Relative Abundance (%)", y = NULL) +
	scale_color_manual(name = "Treatment",
			   labels = c('Control', 'Selection'),
			   values = c('gray40', 'darkorange2')) +
	scale_fill_manual(name = "Treatment",
			   labels = c('Control', 'Selection'),
			   values = c('gray40', 'darkorange2')) +
    facet_grid(direction ~ ., scale = "free_y", space = "free")  +
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank()
) +
	scale_x_log10(breaks = c(0.001, 0.01, 0.1, 1),
		      labels = c(0.001, 0.01, 0.1, 1)))

@@

ggsave(here(fig_dir, 'fig4.png'), p_log10_cl, 
       width = 100, 
       height = 88,
       units = 'mm')
# ggsave(here(fig_dir, 'fig5.svg'), p_log10, width = 5, height = 5)
# ggsave(here(fig_dir, 'fig5_cl.png'), p_log10_cl, width = 5, height = 5)
(p_log10_bw <-
	all_taxa %>%
	ggplot(aes(x = rel_abund, y = Family, fill = treat)) +
	geom_point(position=position_jitterdodge(jitter.width = 0.1,
	                                         dodge.width = 0.4), shape = 21, size = 1) +
        theme_bw(base_size = 7) +
            theme(panel.border = element_rect(fill = NA, linewidth = 1.0625),
                  axis.line = element_blank(),
                  text = element_text(family = 'Arial')) +
	# geom_jitter(shape = 21, height = 0.1) +
	# geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, color = treat), 
	# 		data = all_iqm, 
	# 		position = position_dodge(width = 0.75), 
	# 		shape = 21, 
	# 		# color = "black"
	# 		) +
	# theme_bw() +
	theme(axis.text.y = element_markdown()) +
	labs(x = "Relative Abundance (%)", y = NULL) +
	# scale_color_manual(name = "Treatment",
	# 		   labels = c('Control', 'Selection'),
	# 		   values = c('black', 'gray')) +
	scale_fill_manual(name = "Treatment",
			   labels = c('Control', 'Selection'),
			   values = c('white', 'black')) +
    facet_grid(direction ~ ., 
               scale = "free_y",
               space = "free")  + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank()) +
	scale_x_log10(breaks = c(0.001, 0.01, 0.1, 1),
		      labels = c(0.001, 0.01, 0.1, 1))
    )
# ggsave(here(fig_dir, 'fig5.eps'), 
#        p_log10_bw, 
#        width = 100, 
#        height = 88,
#        units = 'mm',
#        device = cairo_ps
#        )

@@

# Functional gene analysis with Picrust

```{r, eval=FALSE}

metacyc_pathways <- read_tsv(here(der_dir, 'picrust2_out_pipeline/pathways_out/path_abun_unstrat.tsv.gz'))
metacyc_pathways <- metacyc_pathways[,1:49]
metacyc_pathways <- as.data.frame(metacyc_pathways)
rownames(metacyc_pathways) <- metacyc_pathways[, 1]
metacyc_pathways <- metacyc_pathways[, -1]
metadata <- data.frame(conds = substr(colnames(metacyc_pathways), 3, 3))
rownames(metadata) = colnames(metacyc_pathways)
sample_data = sample_data(metadata)
otu_table = otu_table(metacyc_pathways, taxa_are_rows = TRUE)
metacyc_ps <- phyloseq(otu_table, sample_data)
taxa_names(metacyc_ps)
# Save/Load output so you don't have to rerun ANCOM
if(file.exists(here(der_dir, "ancom_out_metacyc.rds"))) {
  out <- 
    readRDS(here(der_dir, "ancom_out_metacyc.rds"))
} else {
  # Run Ancom
  out = ancom(data = metacyc_ps,  
              p_adj_method = "BH",
              prv_cut = 0.1, 
              lib_cut = 0, 
              main_var = "conds",
              rand_formula = NULL, 
              lme_control = NULL,
              struc_zero = TRUE, 
              neg_lb = FALSE, 
              alpha = 0.05, 
              n_cl = 1)  
  out %>% 
    saveRDS(here(der_dir, "ancom_out_metacyc.rds"))
}

res = out$res
q_val = out$q_data
beta_val = out$beta_data
# Only consider the effect sizes with the corresponding q-value less than alpha
beta_val = beta_val * (q_val < 0.05) 
# Choose the maximum of beta's as the effect size
beta_pos = apply(abs(beta_val), 2, which.max) 
beta_max = vapply(seq_along(beta_pos), function(i) beta_val[beta_pos[i], i],
                  FUN.VALUE = double(1))
# Number of taxa except structural zeros
n_taxa = ifelse(is.null(out$zero_ind), 
                ntaxa(metacyc_ps), 
                sum(apply(out$zero_ind[, -1], 1, sum) == 0))
# Cutoff values for declaring differentially abundant taxa
cut_off = 0.7 * (n_taxa - 1)

df_fig_w = res %>%
  dplyr::mutate(beta = beta_max,
                direct = case_when(
                  detected_0.7 == TRUE & beta > 0 ~ "Positive",
                  detected_0.7 == TRUE & beta <= 0 ~ "Negative",
                  TRUE ~ "Not Significant"
                  )) %>%
  dplyr::arrange(desc(W))
df_fig_w$taxon = factor(df_fig_w$taxon, levels = df_fig_w$taxon)
df_fig_w$W = replace(df_fig_w$W, is.infinite(df_fig_w$W), n_taxa - 1)
df_fig_w$direct = factor(df_fig_w$direct, 
                     levels = c("Negative", "Positive", "Not Significant"))

p_w = df_fig_w %>%
  ggplot(aes(x = taxon, y = W, color = direct)) +
  geom_point(size = 2, alpha = 0.6) +
  labs(x = "Taxon", y = "W") +
  scale_color_discrete(name = NULL) + 
  geom_hline(yintercept = cut_off, linetype = "dotted", 
             color = "blue", linewidth = 1.5) +
  geom_text(aes(x = 2, y = cut_off + 0.5, label = "W[0.7]"), 
            size = 5, vjust = -0.5, hjust = 0, color = "orange", parse = TRUE) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major = element_blank())
p_w

ancom_taxa <- as.character(df_fig_w[df_fig_w$detected_0.7, ]$taxon)
metacyc_pathways_descrip <- read_tsv(here(der_dir, 'picrust2_out_pipeline/pathways_out/path_abun_unstrat_descrip.tsv.gz')) %>% 
    select(pathway, description)
metacyc_pathways_descrip[metacyc_pathways_descrip$pathway %in% ancom_taxa,] ->
    sig_pathways
```
